\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2020-01-23 sections/results.tex
Update methods and results

  \begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figure3.pdf}
    \caption{
      \textbf{The representative sequences generated by the different denoising/clustering methods are very similar but differ in the sequences that are in low abundance.}
      \textbf{(A)} The average weighted UniFrac distance between the representative sequences shows that the representative sequences and their compositions are fairly identical between the methods,
      \textbf{(B)} The relatively larger average unweighted UniFrac distance indicates that methods differ in their identification of sequences of low abundance,
      \textbf{(C)} The distributions of the average unweighted UniFrac distance between the expected sequence profile and the calculated sequence profile in mock datasets show that dada2 and Deblur were the best performing methods in most of the datasets.
    }
    \label{fig:figure3}
  \end{figure}

>>>>

  \begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figure3.pdf}
    \caption{
      \textbf{The representative sequences generated by the different denoising/clustering methods are very similar but differ in the sequences that are in low abundance.}
      \textbf{(A)} The average weighted UniFrac distance between the representative sequences shows that the representative sequences and their compositions are fairly identical between the methods,
      \textbf{(B)} The relatively larger average unweighted UniFrac distance indicates that methods differ in their identification of sequences of low abundance,
      \textbf{(C, D)} The distributions of the avergage weighted UniFrac distance between the expected sequence profile and the calculated sequence profile in mock datasets.
      \textbf{(D)} The distributions of the average unweighted UniFrac distance show that dada2 and Deblur were the best performing methods in most of the datasets.
    }
    \label{fig:figure3}
  \end{figure}
